---
title: decs922 R package
author: Robert McDonald
output: github_document
---

This is a package of odds and ends originally created for the class
Data Exploration, DECS-922, at the [Kellogg School of
Management](https://www.kellogg.northwestern.edu/). The package
currently contains

* templates to produce slides and homework assignments; upon package
  installation these are automatically available from RStudio's
  `rmarkdown` templates list. These are a work in progress
* a chunk engine, `soln_notes`, which allows you insert optional text
  within a standalone chunk. When evaluated, the text will be rendered
  in italic and preceded (by default) by `Solution notes`. The
  implementation is functional but buggy.
* the function `colorkey`, which assists with finding an appropriate
  colorname as defined by R. For example, to find a version of
  "orange" which does not contain "red" in the color name, do this:

    ```{r, out.width='70%'}
    library(decs922)
    colorkey(colortext = 'orange', excludetext = 'red')
    ```

* the function `data_summary`, which reports for a data set the number
  of observations, number of missing values, the class of each
  variable, and various summary statistics. Note that there are many
  similar functions available, such as `summary`, `psych::describe`,
  etc. For example, using the built-in dataset `iris`:
  
  ```{r}
  data_summary(iris)
  ```
* the function `translate_datestr`, which parses a string for POSIX
  date codes and returns documentation for the codes (taken from `?strftime`).
  
  ```{r}
  translate_datestr('%Y-%M-%d')
  ```
* `wordle_assist`, which finds 5-letter words that match positional
  inclusions (positive named vector specifying position) and
  exclusions (negative named vector specifying positions. Relies on
  the length-5 words in the [`words` package](https://CRAN.R-project.org/package=words)
  ```{r}
  wordle_assist(no = 'areuntilcump', yes = list(s = c(1, -4), h = 2, o = 3))
  ```




