---
title: decs922
author: Robert McDonald
output: github_document
---

This is a small package for the class Data Exploration, DECS-922, at
the [Kellogg School of
Management](https://www.kellogg.northwestern.edu/). The package
currently contains 

* templates to produce slides and homework assignments; upon package
  installation these are automatically available from RStudio's
  `rmarkdown` templates list. These are a work in progress
* the function `colorkey`, which assists with finding an appropriate
  colorname as defined by R. For example, to find a version of
  "orange" which does not contain "red" in the color name, do this:

    ```{r, out.width='70%'}
    library(decs922)
    colorkey(colortext = 'orange', excludetext = 'red')
    ```

* the function `data_summary`, which reports for a data set the number
  of observations, number of missing values, the class of each
  variable, and various summary statistics. Note that there are many
  similar functions available, such as `summary`, `psych::describe`,
  etc. For example, using the built-in dataset `iris`:
  
  ```{r}
  data_summary(iris)
  ```


