---
title: Tips and Tricks
author: Robert McDonald
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
---

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
opts_chunk$set(error = TRUE)
```



# Do

* Make sure that you always start R with a clean environment. 
  * In RStudio:
    * In "Global Options", ***uncheck*** the box reading "Restore
    .RData into workspace at startup"
    * Set "Save workspace to .RData on exit" to ***Never***
  * In other editors, always answer "n" to the `Save workspace image?
    [y/n/c]` prompt


# Be aware!

* The same function name can be provided by multiple packages. For
  example, `dplyr` uses `filter`, which is also provided by the
  `stats` package, and `summarize` is also provided by the `Hmisc`
  package. If you get an incomprehensible error message associated
  with a dplyr function name, one of the first things to try is to
  qualify the function name. Here is an example in which the first
  calculation fails but the second succeeds.^[It is worth noting that
  standard practice in Python is to qualify function names so that
  this confusion does not occur. For example you `import Pandas as
  pd`, and then call Pandas functions with a `pd.` prefix.]
  
  Note that if you use the British spelling,  `summarise`, this issue
  does not occur. (The `dplyr` package recognizes both spellings, the
  `Hmisc` package does not.)
  
```{r, message=FALSE}
library(Hmisc) ## some other package may have invoked this

mtcars %>% group_by(gear) %>% 
    summarize(N = n())

mtcars %>% group_by(gear) %>% 
    dplyr::summarize(N = n())

mtcars %>% group_by(gear) %>% 
    summarise(N = n())

```



